### 2019-08-02 paper/intro.tex
not spiral

Stars are thought to be born in the thin disk of the Milky Way, orbiting the
center of the galaxy with a low out-of-plane, or vertical, velocity ($W$, or
$v_z$).
Young stars have relatively small vertical velocities, but gain momentum in
the vertical direction over time.
Although the cause of orbital heating is not well understood, interactions
with giant molecular clouds and spiral arms are thought to play an important
role \racomment{(citations)}.
Although the velocity of any individual star will only provide a weak age
constraint, the velocity dispersion of a group of stars can indicate whether,
on average, that group is old or young relative to other groups.
In this work we compare the velocity dispersions of groups of stars to
ascertain which groups are older and which younger and draw conclusions based
on the implied relative ages of populations.
% Stellar velocities have a history of being used as an age proxy, with several
% notable examples within stellar astronomy \citep[\eg][]{faherty2009,
% west2011}.
Since the age-velocity dispersion relations (AVRs) are themselves still
actively being calibrated, it is difficult to directly compare gyrochronal
ages with kinematic ones.
However, regardless of the exact relation between velocity dispersion and
stellar age, it is expected to be a monotonic relationship, therefore velocity
dispersion can be used effectively to {\it rank} groups of stars by age.

>>>>

Stars are thought to be born in the thin disk of the Milky Way, orbiting the
center of the galaxy with a low out-of-plane, or vertical, velocity ($W$, or
$v_z$).
Young stars have relatively small vertical velocities, but gain momentum in
the vertical direction over time.
Although the cause of orbital heating is not well understood, interactions
with giant molecular clouds are thought to play an important
role \racomment{(citations)}.
Although the velocity of any individual star will only provide a weak age
constraint, the velocity dispersion of a group of stars can indicate whether,
on average, that group is old or young relative to other groups.
In this work we compare the velocity dispersions of groups of stars to
ascertain which groups are older and which younger and draw conclusions based
on the implied relative ages of populations.
% Stellar velocities have a history of being used as an age proxy, with several
% notable examples within stellar astronomy \citep[\eg][]{faherty2009,
% west2011}.
Since the age-velocity dispersion relations (AVRs) are themselves still
actively being calibrated, it is difficult to directly compare gyrochronal
ages with kinematic ones.
However, regardless of the exact relation between velocity dispersion and
stellar age, it is expected to be a monotonic relationship, therefore velocity
dispersion can be used effectively to {\it rank} groups of stars by age.
